### 2014-03-29 LaTeX/RhodiumConcl.tex
Short conclusion added. Needs more work.

If NATO had not intervened, the expected duration of the conflict would have been much shorter. But the rebels would have lost, so there is a trade-off.

>>>>

Our project seeks to explain observed discrepencies in the economic impact of civil conflict.  Violent intrastate conflicts have occured in one third of countries in just the past several decades.  While civil wars seem to primarily afflict developing states, their actual economic impacts are still subject to debate.  Some states weather civil conflict for years or even decades while simultaneously prospering economically.  Other states see their economies stall and suffer substantial declines in growth.  Despite this heterogeneity observed among civil war states, the individual characteristics of civil conflict that lead to disparate outcomes have only recently been subject to academic scrutiny.  In this first step of a larger project to distinguish the geography of civil conflict, we hope to have contributed to our understanding of why some civil conflicts impact economic performance more severely than others.  We have used a novel approach in the study of civil conflict to distinguish between spatially dissimilar events and shown that this new measure of interest, the minimum distance between conflict epicenters and major population centers, is a substantive determinant of economic growth.  While the proximity of conflict to major cities helps us to better understand how domestic armed conflict produces disparate economic outcomes across countries, one can imagine a number of other hypotheses that derive from this research.

Population centers are critical to economic performance, but still tell only a part of the story.  States rely on various natural resources as well as critical infrastructure to prosper.  Trade depends on safe and reliable access to ports, airports, and railways.  Businesses rely on safe and reliable access to natural resources.  And foreign direct investment relies on the investor's perception of state stability.  While there is a large literature on natural resources and conflict at the state level, little work has disaggregated this data and explored the micro-relationship between conflict and resources.  Future iterations of this paper will explore each of these hypotheses using geospatial data on the economic assets of interest.

Looking beyond aggregate measures of state economic performance, we hope to further explore how the geography of conflict impacts the surrounding region.  A growing body of work suggests that civil conflict is, in and of itself, contagious.  However, the precise mechanisms that determine contagion risk are still unclear.  We propose that looking at the location of conflict within a state will shed light on how conflicts and their economic effects spread across borders.  The same logic that applies to the hypotheses presented in this paper applies to neighboring states as well.  Resources and population centers that are near the border between a peaceful state and a civil war state may be impacted in the same way that resources and cities within the conflict state are.  This may help to explain the disparate regional economic effects of civil war observed by \cite{murdoch:sandler:2002}.

### 2014-03-29 LaTeX/RhodiumTheory.tex
Short conclusion added. Needs more work.

We suspect that substate factors will determine the economic impacts of civil conflict.  While lootable resources are often pointed to as sources of funding for rebel groups, these same resources are often critical to state economic performance.  The loss of safe access to these resources due to internal conflict should adversly affect a state's economy.  Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.  Therefore, we expect state economic performance to be inversely related to the distance from conflict zones to valuable resources.

@@

Forbes magazine, reporting on peace talks between FARC guerillas and the Colombian government in 2012, wrote: 
\begin{quote}FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government. This has been done by attacking oil and natural gas infrastructure affecting companies such as Pacific Rubiales Energy, Oxy and Ecopetrol. For non-fuel related international companies with subsidiaries in Colombia, such as Goodyear, Nestle, Microsoft, Toyota, among others, FARC’s modus operandi was mainly racketeering, kidnappings and extortion. (Flannery 2012)\end{quote}
By targeting economic centers and resource infrastructure, FARC can strain Colombia's economy, frighten investors, and bolster support from poor and rural workers sensitive to wealth disparity in the country.  Rabasa and Chalk (2001) identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.

>>>>

We suspect that substate factors will determine the economic impacts of civil conflict.  While lootable resources are often pointed to as sources of funding for rebel groups, these same resources are often critical to state economic performance.  The loss of safe access to these resources due to internal conflict should adversly affect a state's economy.  Companies that rely on the extraction of resources may find themselves unable to access those resources if armed conflict is proximately located to the resource sites.  Therefore, we expect state economic performance to be directly related to the distance from conflict zones to valuable resources.

@@

Forbes magazine, reporting on peace talks between FARC guerillas and the Colombian government in 2012, wrote: 
\begin{quote}FARC's strategy and [beliefs have] always been to make economic pressure on both, multinational companies and the Colombian government. This has been done by attacking oil and natural gas infrastructure affecting companies such as Pacific Rubiales Energy, Oxy and Ecopetrol. For non-fuel related international companies with subsidiaries in Colombia, such as Goodyear, Nestle, Microsoft, Toyota, among others, FARC’s modus operandi was mainly racketeering, kidnappings and extortion. (Flannery 2012)\end{quote}
By targeting economic centers and resource infrastructure, FARC can strain Colombia's economy, frighten investors, and bolster support from poor and rural workers sensitive to wealth disparity in the country.  \cite{rabasa:chalk:2001} identify a three-pronged strategy pursued by FARC in the 1990s: to consolidate power in coca-growing regions, to conduct military operations in economically valuable areas, and to isolate major cities from the rest of the country by limiting communication and travel between them.

While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral.  India, for instance, has faced challenges by armed groups in its north-east for half a century.  However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India.  Indeed, for much of this period, India has experienced relatively robust economic growth.

We turn now to an empirical test of our proposition.  Using a dataset that includes 510 instances of civil war from 71 different countries, we seek to determine how the geography of conflict impacts state economic outcomes.
